Species motif participation provides unique information about species risk of extinction

### 2023-05-12 manuscript/JAE_reply.tex
Updates from Overleaf

                \textbf{R:}
                TO DO!

>>>>

                \textbf{R:} Every study we are aware of that relates motifs to stability either models one or more motifs in isolation or examines the effect of motif profiles (or elements thereof, e.g., frequency of omnivory) on the whole network. Neither one is exactly applicable to the effect of motif participation on per-species extinction risk. The exception is an earlier study by some authors of the present work, which we mention but do not wish to over-promote by making this paper a keystone of the introduction. For these reasons, together with constraints of length, we have been judicious in our selection of additional material on previous motif-stability relationships. Particularly for omnivory, the existing literature paints a picture of context-dependence and variable effects rather than a clear general trend. Reviewing this material would be more suited to a general review (perhaps with supplemental modelling to fill gaps between tests of different types of stability, disturbance, etc.) than to a paragraph in our introduction. We hope that the refocusing and revision of the introduction provides enough clarity to compensate for this necessarily cursory overview.

### 2023-05-12 manuscript/reorder_main_text.tex
Updates from Overleaf

% Limit is 8200 words.
% Currently c. 9000
\begin{document} 
\maketitle 
\raggedright

@@

    %There are 13 possible three-species motifs (the most commonly-used size for food web analyses)~\citep{Milo2004,Stouffer2007,Stouffer2012,Cirtwill2015a}, 
    We define motif participation using the well-studied three-species motifs~\citep{Milo2004,Stouffer2007,Stouffer2012,Cirtwill2015a}. 
    Four of these motifs --the three-species chain, apparent competition, direct competition, and omnivory-- are especially interesting as they are by far the most common in empirical networks~\citep{Stouffer2007, giling2019plant} and more stable than other motifs when modelled in isolation~\citep{Borrelli2015a}.
    These four motifs also have clear ecological interpretations.
    The three-species chain indicates vertical flows of energy and biomass in a network and captures the possibility of indirect interactions across multiple trophic levels (e.g., between a plant and a predator of the plant's herbivore).
    The direct competition motif, where two consumers share the same resource, captures the possibility of indirect interactions between consumers (e.g., by depletion of the shared resource). 
    The apparent competition motif, where a predator consumes two resources, can include indirect effects between prey (e.g., by boosting predator populations) in a top-down context, but only includes direct bottom-up interactions.
    Finally, the omnivory motif, where a predator consumes the same resource as its prey, includes captures the potential for a plant to have both direct and indirect effects on the predator.

>>>>

% Limit is 8500 words.
% Currently c. 8066 - we're good!
\begin{document} 
\maketitle 
\raggedright

@@

    %There are 13 possible three-species motifs (the most commonly-used size for food web analyses)~\citep{Milo2004,Stouffer2007,Stouffer2012,Cirtwill2015a}, 
    We define motif participation using the well-studied three-species motifs~\citep{Milo2004,Stouffer2007,Stouffer2012,Cirtwill2015a}. 
    Four of these motifs --the three-species chain, apparent competition, direct competition, and omnivory-- are especially interesting as they are by far the most common in empirical networks~\citep{Stouffer2007, giling2019plant} and more stable than other motifs (i.e., are more likely to retain all three species in the motif) when modelled in isolation~\citep{Borrelli2015a}.
    These four motifs also have clear ecological interpretations.
    The three-species chain indicates vertical flows of energy and biomass in a network and captures the possibility of indirect interactions across multiple trophic levels (e.g., between a plant and a predator of the plant's herbivore).
    The dynamics of three-species chains in isolation are well-understood from Lotka-Volterra models, and stable equilibria with all three species persisting can often be identified~\citep{Borrelli2015a,Hsu2015}.
    In general, food chains are more likely to be stable when predator-prey body-mass ratios are smaller~\citep{Jonsson1998}.
    The direct competition motif, where two consumers share the same resource, captures the possibility of indirect interactions between consumers by depletion of the shared resource in competitive exclusion~\citep{Hsu2015}. 
    Despite the potential for exclusion where one predator is competitively superior, this motif is highly robust to changes in interaction strength and therefore has high quasi-sign stability~\citep{Borrelli2015a}.
    The apparent competition motif, where a predator consumes two resources, can include indirect effects between prey indicates a generalist predator (which may be able persist following reduction or loss of one prey) but can capture indirect effects between prey that mae the predator more likely to go extinct~\citep{Melian2002}.
    Finally, the omnivory motif, where a predator consumes the same resource as its prey, includes captures the potential for a plant to have both direct and indirect effects on the predator. 
    Omnivory is less stable in isolation than the other three motifs~\citep{Borelli2015a}, though there is a region of stable equilibrium for Lotka-Volterra model of omnivory~\citep{Hsu2015}.
    In whole food webs, frequent omnivory has been proposed to both increase and decrease overall stability in different conditions~\citep{McCann1997,Emmerson2004,Monteiro2016}.
    As most of the above studies either model motifs in isolation or examine overall effects on the whole food web, it remains unclear how a particular species' motif participation will affect its specific extinction risk.
